\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{eso-pic}
\usepackage{charter}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\definecolor{gr}{RGB}{225,225,225}

\urlstyle{Same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{4.09pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\fontsize{28}{0}\selectfont Aliaksandr Valchetski}\\ \vspace{1pt}
    \bigbreak
    \href{tel:+48511866698}{\raisebox{-0.1\height}\faPhone\ \underline{+48 511 866 698}} $|$ 
    \href{mailto:alex.volchetsky@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{alex.volchetsky@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/valchetski/}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}} $|$
    \href{https://github.com/valchetski}{\raisebox{-0.2\height}\faGithub\ \underline{GitHub}} $|$
    \href{https://maps.app.goo.gl/fDMVWK2QSbCE37H89}{\raisebox{-0.2\height}\faMapMarker\ \underline{Wrocław, Poland}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
  \resumeSubHeadingListStart
    \resumeItem{Senior Software Engineer (.NET) with 8+ years of experience developing web solutions using ASP.NET.
    Expertise in the setup of CI/CD pipelines. Streamlined deployment processes resulting in a reduction of post-release issues by at least 50\%.}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Software Engineer (.NET)}{ August 2022 - Present}
      {Deltatre}{ Wrocław, Poland}
      \resumeItemListStart
        \resumeItem{Prepared architectural decisions
        for migration from monolith to Microservices for Bell project. Engineered scalable .NET 6 microservices and shared libraries. 
        Splitting of the
        monolithic apps into microservices and the implementation of new features.}
        \resumeItem{Developed Unit Tests via TDD approach to ensure application modules functionality.
        Code coverage reached a minimum of 80\%.}
        \resumeItem{Incorporated TestContainers library to use Mongo and Redis containers in Integration Tests and enable tests in GitHub Actions.
         That boosted code reliability and helped to identify more bugs before deployment to the environments.}
        \resumeItem{Collaborated with the QA team on BDD tests that verify services after deployment,
        resulting in earlier bug identification within staging environments.
        The number of successful releases increased by a minimum of 25\%.}
        \resumeItem{Migrated the CI pipeline to GitHub Actions and created reusable workflows to create builds for the different microservices.}
        \resumeItem{Enhanced deployment process in Octopus to be simpler and less error-prone. As a result, the number of unsuccessful releases decreased by a minimum of 50\%.}
        \resumeItem{Greater involvement in feature planning. Planning, estimation, and delivery of
        big features. Mentoring 2 new team members.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Software Engineer (.NET)}{ May 2021 - July 2022}
      {Deltatre}{ Minsk, Belarus}
      \resumeItemListStart
        \resumeItem{Collaborated with the Bell Canada. Supported and implemented new features for Crave, CTV, Noovo, TSN, and RDS brands, which are OTT solutions in entertainment and sports with 3+ million subscribers.}
        \resumeItem{Constant checking and improving product behavior based on monitoring, logs, and SonarQube reports. Performing releases in Octopus.}
        \resumeItem{All projects were on C\# (.NET 6 and .NET Framework 4.7) and Node.js, using MS SQL Server, MongoDB, and Redis, and hosted on AWS.} 
        \resumeItem{Integrated the Datadog SRE platform with .NET and Node.js projects. 
        Wrote a tool for the creation of monitors and synthetic tests, which helped other teams to have Datadog setup in 1 to 2 days.}
    \resumeItemListEnd

    \resumeSubheading
      {ASP.NET Developer}{ June 2018 - May 2021}
      {Brimit}{ Minsk, Belarus}
      \resumeItemListStart
        \resumeItem{Implemented from scratch and supported Sitecore CMS projects. Built the structure of the new projects using Sitecore Helix architectural principles (modular architecture with 3 layers).}
        \resumeItem{Developed classical ASP.NET MVC 5 projects and also projects with the Sitecore JSS Headless CMS approach (separate FE app and ASP.NET Core GraphQL API) hosted in Azure.}
        \resumeItem{Designed separate Microservices on ASP.NET Core 5 that simplified code maintenance and enhanced deployment speed.}
        \resumeItem{Configured CI/CD pipelines for new and existing projects using Azure DevOps, Octopus, and TeamCity. Adding of CI/CD pipeline to a project, that used manual deployment previously, reduced the number of deployment issues by 70\%.}
      \resumeItemListEnd

    \newpage

    \resumeSubheading
      {ASP.NET Developer}{ March 2016 - June 2018}
      {Elilink Consulting}{ Minsk, Belarus}
      \resumeItemListStart
        \resumeItem{Collaborated with Siemens on the Camstar MES system, which optimizes manufacturing processes and operations on the shop floor in the medical device, semiconductor, and electronics industries for more than 500 clients.}
        \resumeItem{Had a sense of what the big projects look like. Has learned to see the bottlenecks in the code. Collaborated in a big team with more than 50 members.}
        \resumeItem{While fixing bugs improved skills of reading and understanding of the code written by others. Migrated existing components from WebForms to ASP.NET MVC 5 (.NET Framework 4.7).}
      \resumeItemListEnd

    \resumeSubheading
      {ASP.NET Developer}{ November 2015 - February 2016}
      {Vizor}{ Minsk, Belarus}
      \resumeItemListStart
        \resumeItem{Engineered enhancements for the apartment rental service based on the nopCommerce eCommerce platform (ASP.NET MVC 5). Gained experience in commercial development and communication with the customer.}
        \resumeItem{Added new functionality and fixed bugs on the back end and the front end, 
        while strengthening knowledge of JavaScript, jQuery, AngularJS, HTML, CSS, C\#, and SQL.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

  \vspace{10mm}
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C\#, SQL, JavaScript, Typescript} \\
     \textbf{Frameworks}{: .NET, ASP.NET Core} \\
     \textbf{Databases}{: MongoDB, MS SQL, Redis} \\
     \textbf{Runtime environments}{: Node.js} \\
     \textbf{CI/CD}{: GitHub Actions, Octopus, Azure DevOps} \\
     \textbf{Cloud}{: AWS, Azure} \\
     \textbf{SRE}{: Datadog} \\
     \textbf{Developer Tools}{: Git, Docker, Terraform} \\
     \textbf{Methodologies}{: Kanban, Agile} \\
     \textbf{Fundamentals}{: Algorithms, Design Patterns, SOLID, REST API} \\      
    }}
 \end{itemize}


%-------------------------------------------
%-----------LANGUAGES-----------
\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{English}{: Full professional proficiency} \\
     \textbf{Belarusian}{: Native} \\
     \textbf{Russian}{: Native} \\
     \textbf{Polish}{: Intermediate proficiency}
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Belarusian State University of Informatics and Radioelectronics}{ Minsk, Belarus}
      {Bachelor's degree, Information Technology}{September 2012 - June 2017}
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}